Combined annotation exploration for SCPCP000006

### 2024-11-13 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
debugging to be able to run in CI: We need to only loop over available samples

---
title: "Combined annotation exploration for SCPCP000006"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params:
  predicted.celltype.threshold: 0.85
  cnv_threshold: 0
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

We extracted from the pre-processed and labeled `Seurat` object from `results/{sample_id}/06_infercnv_HMM-i3_SCPCS000169_reference-both.rds`.
the following information per cell:

@@

- the proportion of estimated CNV per chromosome, {i} in 1 to 22 `proportion_cnv_chr{i}`

- the `counts`of [markers genes](https://github.com/AlexsLemonade/OpenScPCA-analysis/tree/main/analyses/cell-type-wilms-tumor-06#the-table-celltype_metadatacsv-contains-the-following-column-and-information)

```{r path_to_query}
sample_metadata_file <- file.path(repository_base, "data", "current", "SCPCP000006", "single_cell_metadata.tsv")

metadata <- read.table(sample_metadata_file, sep = "\t", header = TRUE)
sample_ids <- metadata |>
  dplyr::filter(seq_unit != "spot") |>
  dplyr::pull(scpca_sample_id) |>
  unique()

>>>>

---
title: "Combined annotation exploration for SCPCP000006"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params:
  predicted.celltype.threshold: 0.85
  cnv_threshold: 0
  sample_ids: ""
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

We extracted from the pre-processed and labeled `Seurat` object from `results/{sample_id}/06_infercnv_HMM-i3_{sample_id}_reference-{reference}.rds`.
the following information per cell:

@@

- the proportion of estimated CNV per chromosome, `{i}` in 1 to 22 `proportion_cnv_chr{i}`

- the `counts` of [markers genes](https://github.com/AlexsLemonade/OpenScPCA-analysis/tree/main/analyses/cell-type-wilms-tumor-06#the-table-celltype_metadatacsv-contains-the-following-column-and-information)

```{r path_to_query}
sample_metadata_file <- file.path(repository_base, "data", "current", "SCPCP000006", "single_cell_metadata.tsv")
metadata <- read.table(sample_metadata_file, sep = "\t", header = TRUE)

# Determine which sample ids to loop over, which differs if we are testing
if (params$sample_ids == "") {
  sample_ids <- metadata |>
    dplyr::filter(seq_unit != "spot") |>
    dplyr::pull(scpca_sample_id) |>
    unique()
} else {
  sample_ids <- stringr::str_split_1(params$sample_ids, ",")
  stopifnot(
    "Could not determine the sample_ids from the provided param value." =
      all(sample_ids %in% metadata$scpca_sample_id)
  )
}
